---
title: "purrr functions 2"
author: "DanielH"
date: "August 15, 2018"
output:
  github_document:
    toc: true
    toc_depth: 2
  output:
  html_document: default
  html_notebook:
    theme: readable
  pdf_document: default
  keep_md: yes
---

---

```{r, message=FALSE, echo=FALSE}

library(tidyverse)
library(purrrlyr)
library(magrittr)
library(lubridate)
library(repurrrsive)
library(listviewer)



# save the list
got_chars <- got_chars

```

In this part we will consider a list of lists from the package `repurrrsive`. 

The `gotchars_list` is a list of 30 lists composed of 18 elements(vectors) each

## `map()`, `pluck()`

We want to extract an element from a list.

```{r}
# extract by name
got_chars %>%
  map("id") %>%
  flatten_int()


# extract by position
got_chars %>%
  map(2) %>%
  flatten_int()

# using 'pluck' by name
got_chars %>%
  modify_depth(1, pluck, "id") %>%
  flatten_int()

# using 'pluck' by position
got_chars %>%
  modify_depth(1, pluck, 2) %>%
  flatten_int()

# using magrittr::extract()
got_chars %>%
  modify_depth(1, extract, "id") %>%
  flatten() %>%
  flatten_int()
```

## explore the list

```{r}

# check if elements of the 30 lists are all length 18
got_chars %>%
  every(~length(.x) == 18)

# name the list
list_names <-
  got_chars %>%
  modify_depth(1, pluck, "name") %>%
  flatten_chr()

got_chars <-
  got_chars %>%
  set_names(list_names)

# explore the list
got_chars %>%
  sample(2) %>% 
  str(max.level = 2, list.len = 3)

# extract a named element
got_chars %>%
  extract(c("Theon Greyjoy", "Will")) %>%
  str(list.len = 3)

# extract multiple elements
got_chars[2:4] %>%
  map(extract, c("id", "culture")) %>%  # return a list of 3 vector lists
  map(str, max.level = 1) %>%
  compact()  # remove elements that are NULL
  
```

## `has_element()`

Here we want to see which(named) element of the list contains an element "Bronson Webb" and which one contains "Maester"

```{r}
got_chars %>%
  modify_depth(1, has_element, "Bronson Webb") %>%
  keep(~.x == TRUE)


got_chars %>%
  modify_depth(1, has_element, "Maester") %>%
  keep(~.x == TRUE)
```

It's the 'Will' element.

## `head_while()`

```{r}
got_chars %>%
  modify_depth(1, has_element, "Ironborn") %>%
  keep(~. == TRUE)

got_chars %>%
  modify_depth(1, has_element, "Ironborn") %>%
  head_while(~. == TRUE)

got_chars %>%
  modify_depth(1, has_element, "Norvoshi") %>%
  keep(~. == TRUE)

got_chars %>%
  modify_depth(1, has_element, "Norvoshi") %>%
  head_while(~. == FALSE)

got_chars %>%
  modify_depth(1, has_element, "Ironborn") %>%
  tail_while(~. == FALSE) 

```

## `map_if()`, `map_at()`

```{r}
# map_if
got_chars %>%
  modify_depth(1, map_if, is_integer, sqrt) %>%     #sqrt of integer elements
  modify_depth(1, extract, "id") %>%     # extract the square roots, 'id'
  modify_depth(1, flatten_dbl) %>%     # remove one level of hierarchy
  unname() %>%    # remove list names
  as_vector() %>%    # convert to vector
  round(2) 


# map_to
got_chars %>%
  modify_depth(1, map_at, "gender", str_count) %>%    #count gender characters
  modify_depth(1, extract, "gender") %>%     # extract the gender elements
  modify_depth(1, flatten_int) %>%     # remove one level of hierarchy
  unname() %>%      # remove list names
  as_vector() %>%     # convert to vector
  map_chr(~if_else(. == 4, "female", "male"))    # back to character vec
 
```

## from list to dataframe

```{r}

# create tibble
got_chars_tibble <-
  got_chars %>% {
  tibble(name = map_chr(., "name"),
         culture = map_chr(., "culture"),
         gender = map_chr(., "gender"),
         id = map_int(., "id"),
         born = map_chr(., "born"),
         alive = map_lgl(., "alive"))
  }


# set NAs in the culture column
got_chars_tibble <-
  got_chars_tibble %>%
  mutate(culture = parse_character(culture, na = c("", "NA" )))


```







