---
title: "purrr functions"
author: "DanielH"
date: "August 13, 2018"
output:
  github_document:
    toc: true
    toc_depth: 2
  output:
  html_document: default
  html_notebook:
    theme: readable
  pdf_document: default
  keep_md: yes
---

---

An exploration of the R Package `purrr` and its functions. The package is a complete and consistent functional programming toolkit for R.

Here we consider two cases:

* a list of dataframes
* a list of lists


```{r, message=FALSE, echo=FALSE}

library(tidyverse)
library(purrrlyr)
library(lubridate)
library(listviewer)

# read all files in the directory and store in a list
specdata_list <-
  list.files("specdata", full.names = TRUE) %>%
  map(read_csv, 
      cols(Date = col_date(),
           sulfate = col_double(),
           nitrate = col_double(),
           ID = col_integer()),
      col_names = T)  

```

## `modify_depth()`

>`modify_depth()` only modifies elements at a given level of a nested data structure.

```{r}
## extract date column for each element, for example element 88

# case one
set.seed(0841)
specdata_list %>%
  .[88] %>%           # here we select list 88 containing a df
  modify_depth(1, select, Date) %>%
  modify_depth(1, sample_n, 3)

# case two
set.seed(0841)
specdata_list %>%
  .[[88]] %>%  # here we select df 88
  select(Date) %>%
  sample_n(3)
  

# extract ID col, print first 3 rows, convert to vector, remove names
set.seed(0841)
specdata_list %>%
  sample(3) %>%         # 3 random elements of the list
  modify_depth(1, select, ID) %>%              # select ID in each element
  modify_depth(1, head, 3) %>%               # first 3 rows for each element
  modify_depth(1, as_vector) %>%         # convert the dfs to vectors
  modify_depth(1, unname) %>%             # to unnamed vectors
  flatten() %>%        # remove one level
  as_vector()        # make it a single vector



#--------------- compute number of rows for each element of the list, dfs
# custom function
sel_col1 <- function(x) {
  x %>%
    dim() %>% 
    .[1]
}

# map function
specdata_list[203:206] %>% 
  modify_depth(1, sel_col1)

# equivalently
specdata_list[203:206] %>%
  modify_depth(1, nrow)
  
```

## `every()`, `some()`

>Do every or some elements of a list satisfy a predicate?

```{r}

# check whether ALL element names always the same & matching the vector
specdata_list %>%
  modify_depth(1, names) %>%   # extract df names
  every(~.x %in% c("Date", "sulfate", "nitrate", "ID"))


# check whether ALL element names are partially matching the vector
specdata_list %>%
  modify_depth(1, names) %>%   # extract df names
  flatten_chr() %>% 
  every(~.x %in% c("Date", "sulfate", "whatever", "ID"))

# check whether some element names are matching the vector
specdata_list %>%
  modify_depth(1, names) %>%   # extract df names
  flatten_chr() %>% 
  some(~.x %in% c("Date", "sulfate", "bullo", "ID"))


# check whether some ID cols contain the value: '14'
specdata_list %>%
  modify_depth(1, select, ID) %>%      # list of 331 dfs
  map(as_vector) %>%       # list 331 vectors
  map(unname) %>%        # 331 unnamed vectors
  flatten_int() %>%      # single integer vector, length 332
  some(~. == 14)


# check whether some ID cols contain the value: '18565'
specdata_list %>%
  modify_depth(1, select, ID) %>%     # list of 331 dfs
  map(as_vector) %>%      # list 331 vectors
  map(unname) %>%      # 331 unnamed vectors
  flatten_int() %>%     # single integer vector, length 332
  some(~. == 18565)

```


## `keep()`, `discard()`

>Keep or discard elements using a predicate function

```{r}
## check how many cases we have for which ID == 34
# method 1
specdata_list %>%
  modify_depth(1, select, ID) %>%     # return list of 332 'ID' tibbles
  modify_depth(1, as_vector) %>%     # extract list of 332 'ID' vectors
  modify_depth(1, unname) %>%        # remove names from each vector
  flatten_int() %>% 
  keep(~. == 34) %>%
  length()
  
# method 2 
specdata_list %>%
  modify_depth(1, pull, ID) %>%       # return list of 332 'ID' vectors
  flatten_int() %>%             # return a single vector, length 332
  keep(~. == 34) %>% 
  length()

# method three
specdata_list %>%
  modify_depth(1, pull, 4) %>%
  flatten_int() %>%        # return a single vector, length 332
  keep(~. == 34) %>% 
  length()

# verify previous three 
specdata_list %>%
  .[[34]] %>%        # extract 34th dataframe
    dim() %>%         # rows and cols
  .[1]               # extract rows


## Same cases as above but using discard()
# method 1
specdata_list %>%
  modify_depth(1, select, ID) %>%       # return list of 332 'ID' tibbles
  modify_depth(1, as_vector) %>%       # extract list of 332 'ID' vectors
  modify_depth(1, unname) %>%         # remove names from each vector
  flatten_int() %>% 
  discard(~. != 34) %>%
  length()

# method 2 
specdata_list %>%
  modify_depth(1, pull, ID) %>%         # return list of 332 'ID' vectors
  flatten_int() %>%                 # return a single vector, length 332
  discard(~. != 34) %>% 
  length()
```

## `modify_if()`, `modify_at()`

> `modify_if()` only modifies the elements of x that satisfy a predicate and leaves the others unchanged. 

>`modify_at()` only modifies elements given by names or positions.  

```{r}

# modify the numeric col 'ID'
specdata_list %>%
  modify_depth(1, na.omit) %>%
  modify_depth(1, modify_if, is.numeric, ~.x + 1) %>%
  .[[5]] %>%
  sample_n(3)


# modify col 'ID'
specdata_list %>%
  modify_depth(1, na.omit) %>%
  modify_depth(1, modify_at, "ID", ~sqrt(.x) + 1) %>%
  .[[5]] %>%
  sample_n(3)
  

# modify col 'sulfate'
specdata_list %>%
  modify_depth(1, na.omit) %>%
  modify_depth(1, modify_at, "sulfate", ~sqrt(.x) + 10) %>%
  .[[5]] %>%
  sample_n(3)

# modify col 'nitrate'
specdata_list %>%
  modify_depth(1, na.omit) %>%
  modify_depth(1, modify_at, "nitrate", ~sqrt(.x) + 10) %>%
  .[[265]] %>%
  sample_n(3)

# modify col 'nitrate' and 'sulfate'
specdata_list %>%
  modify_depth(1, na.omit) %>%
  modify_depth(1, modify_at, c("nitrate", "sulfate"), ~sqrt(.x) + 100) %>%
  .[[265]] %>%
  sample_n(3)

# modify at col 'Date'
specdata_list %>%
  modify_depth(1, na.omit) %>%
  modify_depth(1, modify_at, "Date", month, 
               label = TRUE, abbr = FALSE) %>%
  .[[113]] %>%
  sample_n(3)

# modify if col type Date
specdata_list %>%
  modify_depth(1, na.omit) %>%
  modify_depth(1, modify_if, is.Date, year) %>%
  .[[113]] %>%
  sample_n(3)
```

## `head_while()`, `tail_while()`

We can use this construct to figure out the length of each element (df) of the list. For example:

```{r}

# using head_while
specdata_list %>%
  modify_depth(1, pull, ID) %>%
  flatten_int() %>%
  head_while(~. == 1) %>% 
  length()

# verify
specdata_list %>%
  .[[1]] %>%
  dim() %>%
  .[1]

# using tail_while
specdata_list %>%
  modify_depth(1, pull, ID) %>%
  flatten_int() %>%
  tail_while(~. >= 332) %>% 
  length()

# verify
specdata_list %>%
  .[[332]] %>%
  dim() %>%
  .[1]  
```

## `pluck()`

```{r}

# create a named list
list_names <- seq(1:332)

specdata_list_named <-
  specdata_list %>%
  set_names(list_names)


specdata_list_named[222:224] %>%
  pluck("224") %>%
  sample_n(3)

# here pull and pluck are equivalent
sub_list1 <-
  specdata_list[22:24] %>%
  modify_depth(1, pluck, 1)

sub_list2 <-
  specdata_list[22:24] %>%
  modify_depth(1, pull, 1)
# check
sub_list1 %>% 
  identical(sub_list2)


specdata_list[223:225] %>%
  modify_depth(1, names) %>%
  modify_depth(1, str_to_upper)

# using attr_getter()
dfs <- 
  list(iris, mtcars)

dfs %>%
  str(max.level = 1)

dfs %>% 
  pluck(2, attr_getter("row.names")) %>%
  sample(5)

dfs %>%
  pluck(1, attr_getter("row.names")) %>%
  sample(5)
  
```

### more on col names matching

## `negate()`

Here we want to match our character vector `c("Date", "sulfate", "nitrate", "ID")` x 20
to a character vector like this: `c("Date", "sulfate", "ID")`
We have a total of 80 elements of a list/vector, and `nitrate` (that is 1/4 of total cases) doesn't match the predicate `~.x %in% c("Date", "sulfate", "ID")`

Using keep/discard, we remove all the `nitrate` cols 

```{r}
rep(c("Date", "sulfate", "nitrate", "ID"), 20) %>% 
  #as.list() %>% 
  keep(negate( ~.x %in% c("Date", "sulfate", "ID")))  
  
  
rep(c("Date", "sulfate", "nitrate", "ID"), 20) %>% 
  #as.list() %>% 
  discard(~.x %in% c("Date", "sulfate", "ID")) 
```



