---
title: "Untitled"
author: "DanielH"
date: "August 17, 2018"
output:
  github_document:
    toc: true
    toc_depth: 2
  output:
  html_document: default
  html_notebook:
    theme: readable
  pdf_document: default
  keep_md: yes
---

---

```{r}
library(tidyverse)
library(purrrlyr)
library(magrittr)
library(jsonlite)
library(lubridate)
library(repurrrsive)
library(listviewer)

# read data
nyfood_dat <- 
  fromJSON("retail_food_markets.json")
```

## The dataset

```{r}
nyfood_dat %>%
  str(max.level = 1)
```

As we can see our list, `nyfood_dat` has 2 components, two lists:

* `meta`

* `data`

We start exploring the `data` component

```{r}

# extract data component
nyfood_sub_data <-
  nyfood_dat %>%
  pluck("data")

# check whether each element has length 23
nyfood_sub_data %>%
  every(~length(.x) == 23)

# some exploration
nyfood_sub_data[[5]] %>% 
  str(max.level = 1)
```

We can see the data but we need to know what they refer to. We now explore the `meta` component, looking for 23 names stored somewhere

```{r}
# extract meta component
nyfood_sub_meta <-
  nyfood_dat %>%
  pluck("meta")

nyfood_sub_meta %>%
  str(max.level = 2)

```

We see that there's an element `columns`, a dataframe containing 23 observations. we extract it and then extract the column `name`

```{r}
# extract and store names in a vector nms 
nms <-
  nyfood_sub_meta %>%
  pluck("view") %>%
  pluck("columns") %>%
  pull(name)
```

Back to our data component of the original list

```{r}


nyfood_sub_data <-
  nyfood_sub_data %>%
  modify_depth(1, set_names, nms)


nyfood_data <- nyfood_sub_data


nyfood_data_df <-
  nyfood_data %>% 
  {tibble(county = map_chr(., "County"),
          operation_type = map_chr(., "Operation Type"),
          entity_name = map_chr(., "Entity Name"),
          dba_name = map_chr(., "DBA Name"),
          street_number = map_chr(., "Street Number", 
                                  .null = NA_character_),
          street_name = map_chr(., "Street Name"),
          city = map_chr(., "City"),
          state = map_chr(., "State"),
          zip_code = map_chr(., "Zip Code"))}

nyfood_data_df <-
  nyfood_data_df %>%
  dmap_if(is_character, str_to_lower)

nyfood_data_df <-
  nyfood_data_df %>%
  select(state, county, city, zip_code, everything()) %>%
  dmap_at(c(1:5), factor)


# trim cols where required
nyfood_data_df <-
  nyfood_data_df %>%
  dmap_at(c(3, 6, 7), str_trim, "right") 


# define data manipulation function
total_by <-
  function(var) {
    var <- enquo(var)
    nyfood_data_df %>%
      group_by(!!var) %>%
      summarize(total = n()) %>%
      arrange(desc(total))
  }
    

# call function
total_by(city) %>% head(4)
total_by(county) %>% head(4)
total_by(zip_code) %>% head(4)


# define plot function
total_by(city) %>%
  head(30) %>% 
  ggplot(aes(fct_reorder(city, total), total)) +
  geom_point(color = "red") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Total stores by city",
       x = "", y = "")

```

Now we try to look at list-columns, 




